\documentclass[12pt,a4paper,oneside]{report}

\usepackage{titlesec}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{booktabs, chemformula}
\usepackage{titlesec, blindtext, color}
\newcommand\tab[1][1cm]{\hspace*{#1}}

 \geometry{
 a4paper,
 top=35mm,
bottom=30mm,
bindingoffset=0.0in
 }
\pagenumbering{arabic} 

\pagestyle{headings}

\newcommand{\dspaceon}{\renewcommand{\baselinestretch}{1.3}\large\normalsize}
\newcommand{\dspaceoff}{\renewcommand{\baselinestretch}{1}\large\normalsize}

\graphicspath{ {images/} }

\definecolor{gray75}{gray}{0.75}
\newcommand{\hsp}{\hspace{20pt}}
\titleformat{\chapter}[hang]{\Large\bfseries}{\thechapter\hsp\textcolor{gray75}{$|$}\hsp}{0pt}{\Large\bfseries}
\titleformat{\section}{\normalfont\large\bfseries}{\thesection}{1em}{}


\begin{document}
\input{Title.tex}

\tableofcontents

\newpage

\include{Introduction}

\include{TheoreticAspects}

\include{ToolDescription}

\include{Implementation}

\include{ExperimentalResults}

\chapter{Conclusions}


\begin{thebibliography}{1}

\bibitem{ct1}
David Binkley, \emph{Source Code Analysis: A Road Map}, Future of Software Engineering, 2007. FOSE '07.
\bibitem{ct8}
N. Ajienka and A. Capiluppi, \emph{Understanding the interplay between the logical and structural coupling of software classes}, J. Systems Software, vol. 134, pp. 120-137, 2017.
\bibitem{ct6}
Igor Wiese, Rodrigo Kuroda, Reginaldo Re, Gustavo Oliva, Marco Gerosa, \emph{An Empirical Study of the Relation Between Strong Change Coupling and Defects Using History and Social Metrics in the Apache Aries Project}, IFIP International Conference on Open Source Systems, OSS 2015: Open Source Systems: Adoption and Impact, pp. 3-12.
\bibitem{ct2}
G. Booch, \emph{Object-Oriented Analysis and Design with Applications}, Third Edition: Addison-Wesley, 2007.
\bibitem{ct3}
Marcelo Cataldo, Audris Mockus, Jeffrey A. Roberts, and James D. Herbsleb, \emph{Software Dependencies, Work Dependencies, and Their Impact on Failures},  IEEE Transactions on Software Engineering ( Volume: 35, Issue: 6, Nov.-Dec. 2009 ), pp. 864-878.
\bibitem{ct4}
Beck F., Diehl S.,\emph{ On the congruence of modularity and code coupling}, In ESEC/FSE'11: European Software Engineering Conference and Symposium on Foundations of Software Engineering (2011), pp. 354-364.
\bibitem{ct5}
Liguo Yu,\emph{Understanding component co-evolution with a study on Linux}, Empirical Software Engineering, April 2007, Volume 12, Issue 2, pp. 123-141.
\bibitem{ct7}
 Ben Collins-Sussman, Brian W. Fitzpatrick, and C. Michael Pilato, \emph{Version Control with Subversion}, http://svnbook.red-bean.com/en/1.7/svn.basic.version-control-basics.html, 2008.
\bibitem{ct9}
 Huzefa Kagdi, Malcom Gethers, Denys Poshyvanyk, Michael L. Collard,\emph{Blending Conceptual and Evolutionary Couplings to Support Change Impact Analysis in Source Code}, 17th Working Conference on IEEE, 2010, pp. 119-128.
\bibitem{ct10}
Poshyvanyk, Denys, \emph{Using information retrieval based coupling measures for impact analysis}, Empirical Software Engineering 14 ,2008, pp. 5-32.
\bibitem{srcml1}
Collard, M. L., Kagdi, H., and Maletic, J. I., \emph{An XML-Based Lightweight C++ Fact Extractor}, IEEE International Workshop on Program Comprehension (IWPC'03), Portland, OR, May 10-11 2003, pp. 134-143
\bibitem{srcml2}
Collard, M.L., Decker, M., Maletic, J. I.,  \emph{Lightweight Transformation and Fact Extraction with the srcML Toolkit}, IEEE International Working Conference on Source Code Analysis and Manipulation (SCAM'11), 2011, pp. 173-184.
\end{thebibliography}


\end{document}










